Codebook created on 2021-06-11 at 2021-06-11 08:13:01

### 2021-06-12 codebook_df.Rmd
update analyses

---
title: "Codebook created on 2021-02-15 at 2021-02-15 10:15:54"
output: github_document
---

@@

## Dataset description
The data contains 2411 cases and 25 variables.

>>>>

---
title: "Codebook created on 2021-06-11 at 2021-06-11 08:13:01"
output: github_document
---

@@

## Dataset description
The data contains 2643 cases and 25 variables.
